---
title: "p8105_HW1_rkm2147"
author: "Ronae McLin"
date: "9/16/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Be sure to load tidyverse into library in order to use tibble tool
```{r}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:

- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”


```{r create_df}
prob1_df =
    tibble(
      samp = rnorm(10),
      samp_gt_0 = samp > 0,
      char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
      factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod","high", "high", "high"))
    )
```


Try to take the mean of each variable:
```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

What worked and what didn't work?


Variable Worked   |   Variable did not work
------------------|------------------------
   samp           |   char_vec
 samp_gt_0        |   factor_vec


Next step: 
- convert the logical vector to numeric, and multiply the random sample by the result
- convert the logical vector to a factor, and multiply the random sample by the result
- convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
                   
```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```
              
## Problem 2

We are now using the penguin data set

```{r}
data("penguins", package = "palmerpenguins")
```


The data `r data(penguins) ` includes a total of 8 variables of importance: `r variable.names(penguins) `. 

The data ` (penguins) ` size is `r nrow(penguins) ` rows by `r ncol(penguins) ` columns.  

The mean flipper length for the penguin data set is `r mean (penguins) `  

Make a scatter plot! Using bill length and flipper length as variables. 

```{r}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species))
```

