---
title: "p8105_HW1_rkm2147"
author: "Ronae McLin"
date: "9/16/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Be sure to load tidyverse into library in order to use tibble tool
```{r}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:

- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”


```{r create_df}
prob1_df =
    tibble(
      samp = rnorm(10),
      samp_gt_0 = samp > 0,
      char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
      factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod","high", "high", "high"))
    )
```


Try to take the mean of each variable:
```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

What worked and what didn't work?


Variable Worked   |   Variable did not work
------------------|------------------------
   samp           |   char_vec
 samp_gt_0        |   factor_vec


Next step: 
- convert the logical vector to numeric, and multiply the random sample by the result
- convert the logical vector to a factor, and multiply the random sample by the result
- convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
                   
```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```
              
## Problem 2

We are now using the penguin data set

```{r penguin data}
data("penguins", package = "palmerpenguins")
```


The data set includes a total of 8 variables of importance: `r variable.names(penguins) `.

When considering the summary report, we notice that Chinstrap penguins have the smallest amount of penguin numbers, and that the island of Torgersen has the smallest amount of penguins. Efforts could be concentrated in these two areas.  
```{r summary}
summary(penguins)
```

The penguin data set size is `r nrow(penguins) ` rows by `r ncol(penguins) ` columns.  

The mean flipper length for the penguin data set is `r mean(penguins[["flipper_length_mm"]])`   

Make a scatter plot! Using bill length and flipper length as variables. 

```{r scatterplot}
ggplot(data = penguins) + 
  geom_point(mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species))
```

