---
title: "p8105_HW1_rkm2147"
author: "Ronae McLin"
date: "9/16/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Be sure to load tidyverse into library in order to use tibble tool
```{r}
library(tidyverse)
```

## Problem 1

Create a data frame comprised of:

- a random sample of size 10 from a standard Normal distribution
- a logical vector indicating whether elements of the sample are greater than 0
- a character vector of length 10
- a factor vector of length 10, with 3 different factor “levels”


```{r create_df}
prob1_df =
    tibble(
      samp = rnorm(10),
      samp_gt_0 = samp > 0,
      char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
      factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod","high", "high", "high"))
    )
```


Try to take the mean of each variable:
```{r}

```

What worked and what didn't work?

Variable Worked   |   Variable did not work
_________________ |__________________________
                  |
                  |
                  
                  
## Problem 2

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
